Poincar\'e--Friedrichs constants over triangulated domains

### 2024-04-29 main.tex
Update on Overleaf.

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

@@

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}
\usepackage{amscd}
\usepackage{tikz-cd}
\newtheorem{remark}{Remark}

@@

\begin{remark}
    Suppose that $\calT$ is a simplicial complex and that $T$ is a simplex, $T \notin \calT$, such that $\calS := T \cap |\calT|$ is a subcomplex of $\partial T$. 
    According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
    \begin{align*}
        \begin{CD}
            \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT \cup T) \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
        \end{CD}
    \end{align*}
    We notice that $\calS$, $\calT$, $T$ and $\calT \cup T$ are each connected, and hence their zeroth homology groups are isomorphic to $\bbZ$. 
    By the nature of the mappings in the Mayer-Vietoris sequence, we see that 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT \cup T) \longrightarrow 0 
        \end{CD}
    \end{align*}
    is an exact sequence. 
    Moreover, $H_{k}(\calS) = H_{k}(T) 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
    the Mayer-Vietoris sequence includes the exact sequence 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT \cup T) \longrightarrow 0 
        \end{CD}
    \end{align*}
    and we conclude that $H_{k}(\calT) = 0$ for $1 \leq k \leq n-1$.
    Finally, the Mayer-Vietoris sequence includes the exact sequences 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT \cup T) \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT \cup T) \longrightarrow 0 
        \end{CD}
    \end{align*}
    Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT \cup T)$.
    % We know that  $H_{0}(\calT \cup T) \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT \cup T)$. 
    % one easily sees that $H_{0}(\calT \cup T) \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT \cup T)$. 
    If $\calS$ is isomorphic to disk,
    then $H_{n}(\calT \cup T) \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT \cup T) \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
    If instead $\calS$ is isomorphic to a sphere, 
    then $H_{n}(\calT \cup T) \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT \cup T) \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
    % Moreover, Thus $H_{n}(\calT \cup T) = H_{n}(\calT) \oplus H_{n}(\calS)$.
    % We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
    % NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT \cup T) \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT \cup T) \longrightarrow 0 
        \end{CD}
    \end{align*}
\end{remark}

A simplicial $n$-dimensional complex $\calT$ is called shellable if its $n$-simplices can be arranged in linear order $T_0, T_1, \dots$ in such a way that the subcomplex $( \cup_{i=0}^{k-1} T_i ) \cap T_k$ has dimension $n-1$ for all $k > 0$.
